### 2020-12-14 README.Rmd
add
change README, add some more state-year equivalents.

- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year data.
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.

>>>>

- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.
